How wide scale deflections (WSDs) corrupt large scale network modelling of resting state fMRI.

### 2020-01-08 manuscript/manuscript.tex
plan for the rest of the MS

\section*{Methods}
\subsection*{Experimental data}

@@

@@

@@

>>>>

\section*{Methods}
Methods here describe the expermiental data and the mentioned dynamical models.

\subsection*{Experimental data}
Here talk about all the datasets that will be used

UCLA Rest
BZ Rest

Talk about various levels of de-noising on standard clinical sets
Non AROMA
AROMA+2P
AROMA+2P+GMR
AROMA+2P+DiCER

Talk about denoising on HCP

MPP
MPP+sICA+FIX
MPP+sICA+FIX+GMR
MPP+sICA+FIX+DiCER

Talk about the strucual connectivity matrix.

@@

Homogenous models:
Balanced EI
Hopf
BTF

Heterogenous Node:
Hopf

Hetergenous Edge:
Hopf+ANEC

@@

Show the results + show carpet plots and stuff

@@

Show how it comes about.
